Structured Versus Decorated Cospans

### 2020-11-17 cospans.tex
polished up material around Theorem 2.3

The remaining properties are coherence diagrams that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $\alpha,\lambda,\rho$ and $\beta$ and the double category structure functors $U$ and $\odot$. We exhibit one of these diagrams to give the reader a sense of how they are verified, with more details able to be found in the second author's thesis \cite{CourserThesis}. The coherence diagram that we will check is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$};
\node (B) at (3,0) {$(N_1 \odot N_2) \otimes (M_1 \odot M_2)$};
\node (C) at (0,-.75) {$(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$};
\node (D) at (3,-.75) {$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\beta$} (B)
(B) edge node[right]{$\chi$} (D)
(A) edge node[left]{$\chi$} (C)
(C) edge node[above]{$\beta \odot \beta$} (D);
\end{tikzpicture}
\]
which expresses that the braiding is a transformation of double categories.

>>>>

The remaining properties are coherence diagrams that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $\alpha,\lambda,\rho$ and $\beta$ and the double category structure functors $U$ and $\odot$. We exhibit one of these diagrams to give the reader a sense of how they are verified, with more details able to be found in the second author's thesis \cite{CourserThesis}. The coherence diagram that we will check is given by:
The remaining properties are coherence laws that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $\alpha,\lambda,\rho$ and $\beta$ and the double category structure functors $U$ and $\odot$. We exhibit one of these laws to give the reader a sense of how they are verified, with more details available in the second author's thesis \cite{CourserThesis}. The coherence law that we check says that this diagram commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$};
\node (B) at (3,0) {$(N_1 \odot N_2) \otimes (M_1 \odot M_2)$};
\node (C) at (0,-.75) {$(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$};
\node (D) at (3,-.75) {$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\beta$} (B)
(B) edge node[right]{$\chi$} (D)
(A) edge node[left]{$\chi$} (C)
(C) edge node[above]{$\beta \odot \beta$} (D);
\end{tikzpicture}
\]
which expresses that the braiding is a transformation of double categories.
